Loop-Aware Optimizations in PyPy's Tracing JIT

### 2011-06-27 talk/iwtc11/paper.tex
fix XXX

We can observe that PyPy (even without loop peeling) is orders of magnitude
faster than either CPython or Psyco. This is due to the JIT compilation
advantages and optimizations we discussed in previous work
\cite{bolz_allocation_2011, bolz_runtime_2011}. Loop
peeling gives an additional XXX on average, which makes benchmark times
comparable with native-compiled C code. Missing performance we attribute to
the relative immaturity of PyPy's JIT assembler backend as well as missing
optimizations, like instruction scheduling.

>>>>

We can observe that PyPy (even without loop peeling) is orders of magnitude
faster than either CPython or Psyco. This is due to the JIT compilation
advantages and optimizations we discussed in previous work
\cite{bolz_allocation_2011, bolz_runtime_2011}. The geometric mean of the
speedup of loop peeling is 70\%, which makes benchmark times
comparable with native-compiled C code. We attribute the performance gap to C code to
the relative immaturity of PyPy's JIT assembler backend as well as missing
optimizations, like instruction scheduling.
